\documentclass{beamer}

\usetheme{Madrid}
\usecolortheme{default}

\title{Integer Programming: MIQP and MILP}
\author{Muhammad Yasirroni}
\institute{Universitas Gadjah Mada}
\date{\today}

\begin{document}

\frame{\titlepage}

\begin{frame}{Introduction}

    \textbf{Optimization}
    
    \begin{itemize}
    \item A process to find the best solution to a problem based on a set of objectives subject to constraints.
    \end{itemize}

    \textbf{Importance of Optimization in Real-World Applications}
    
    \begin{itemize}
    \item Optimization is used in various fields, such as finance, engineering, logistics, healthcare, and many others.
    \item It helps in making better decisions, improving efficiency, reducing costs, and achieving optimal outcomes.
    \end{itemize}
    
\end{frame}
    

\begin{frame}{Example}
    \textbf{Example: Clothing Manufacturing}

    A clothing manufacturer wants to produce summer and winter shirts, both made from cotton. The summer shirts require 2 yards of blue cotton and 3 yards of red cotton to produce. The winter shirts require 3 yards of blue cotton and 1 yard of red cotton to produce.

    The manufacturer has a total of 30 yards of blue cotton and 20 yards of red cotton available to use for production. The profit from selling one summer shirt is \$20, and the profit from selling one winter shirt is \$25.

    The manufacturer wants to maximize their profit from selling the summer and winter shirts, while using no more than the available cotton. How many summer and winter shirts should they produce to achieve this goal?
\end{frame}

\begin{frame}{Linear Programming}
  \begin{itemize}
    \item Definition of linear programming
    \item LP formulation
    \item Solving LP problems using simplex algorithm
    \item LP software tools
  \end{itemize}
\end{frame}

\begin{frame}{Integer Programming}
  \begin{itemize}
    \item Definition of integer programming
    \item IP formulation
    \item Solving IP problems using branch-and-bound algorithm
    \item IP software tools
  \end{itemize}
\end{frame}

\begin{frame}{Mixed-Integer Linear Programming}
  \begin{itemize}
    \item Definition of mixed-integer linear programming
    \item MILP formulation
    \item Solving MILP problems using branch-and-bound algorithm
    \item MILP software tools
  \end{itemize}
\end{frame}

\begin{frame}{Mixed-Integer Quadratic Programming}
  \begin{itemize}
    \item Definition of mixed-integer quadratic programming
    \item MIQP formulation
    \item Solving MIQP problems using branch-and-bound algorithm
    \item MIQP software tools
  \end{itemize}
\end{frame}

\begin{frame}{Case Studies and Applications}
  \begin{itemize}
    \item Examples of real-world problems that can be solved using integer programming
    \item Demonstration of solving a sample problem using software tools
  \end{itemize}
\end{frame}

\begin{frame}{Conclusion and Future Directions}
  \begin{itemize}
    \item Summary of key points
    \item Future directions in optimization
    \item Acknowledgments (if applicable)
  \end{itemize}
\end{frame}

\begin{frame}{References}
  \begin{itemize}
    \item List of references cited in the presentation
  \end{itemize}
\end{frame}

\begin{frame}{Thank You}
  \centering
  \Huge Thank You!
\end{frame}

\end{document}
